Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration

### 2019-12-28 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-28 19-22-26

\subsection{Outline of the algorithm}\label{sec:outline-algorithm}
In a PV array with $s$ PV strings.
For a given current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s})$ $(Q_{i} \geq Q_{j} \mbox{\ if\ } i \leq j)$, we will assign PV panels to strings in the order of $Q_{1},Q_{2},\ldots ,Q_{s}$.
In this step, we will consider how much we lose an opportunity that the panel is more effectively used for the next current level.
For example, as the PV panel shown in Table~\ref{tab:NumofModules} which contain three PV modules.
2 of 3 modules are able to working at current level of $Q_{1}$ and $Q_{2}$.
All 3 modules are able to activate at current level $Q_{3}$.
Thus, if this panel been selected working for a PV string at current level $Q_{1 or 2}$ , two-third of modules are able to deliver energy while the remaining one module been bypassed.
We consider the ``$loss$'' that how many PV modules we fail to use in other current level and the ``$gain$'' that how many PV modules we can activate in the target current level together.
Since two parameter are considered in the selection process, they can minimize ``$loss$'' while minimizing the number of selected PV panels.
% In this algorithm, we select PV panels as so to minimize the $loss$ and maximize the $gain$.
\begin{table}[tbp]
  \caption[]{}
  \label{tab:NumofModules} 
  \centerline{Maximum number of activate PV modules}
  \vskip5pt
  \begin{center}
  \begin{tabular}{c|c|c|c}
    \hline
    Current level                 & $Q_{1}$ & $Q_{2}$ & $Q_{3}$  \\ \hline
    Number of activate PV modules & 2  & 2    & 3        \\ \hline
  \end{tabular}
  \end{center}
\end{table}
In this algorithm, we choose $Loss-rate$ to give selection priority.
The $Loss$-$rate$ is the difference of active modules in panel $p$ for the target current level $Q_n$  in current sequence $Q$ with other current levels per module.
Let $M_{p}(I)$ denote the number of PV modules that can be active at current level $I$ in panel $p$.
In a $s$ strings PV array, $Loss-rate$ for panel $p$ of target current level $n$ on $k$-th current level $Q_{k}$ ($2 \leq k \leq s$) is shown as follow.
\begin{equation}\label{eq:4}
    Loss\mbox{-}rate(p,n,k) =
    \begin{cases}
    \frac{M_{p}(Q_{k})-M_{p}(Q_{n})}{M_{p}(Q_{n})} & \mbox{if } M_{p}(Q_{n}) \neq 0 \\
    \infty & \mbox{if } M_{p}(Q_{n}) = 0
  \end{cases}
\end{equation}

@@

To assign panels of target current level $n$ to $n$-th string, the following step are applied.
Let $m$ be the required number of active modules per-string.
\begin{enumerate}
  \item\label{step:1} Sort un-selected panels with ``$loss$'' and ``$gain$''.
% \item\label{step:1} Sort un-selected panels in a lexicographically ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_p(Q_n)$.
\item\label{step:2} Selects sorted panels one by one until reaching the required number of active modules $m$.
  % In step 2, panel with no active modules is skipped.
\item\label{step:3} Optimize the number of active modules.
  In step 3, if the number of selected active modules exceeds the required number $m$, redundant panels will be removed if exist.
\end{enumerate}
% \begin{table*}[h]
%   \caption[]{ \label{tab:Exampleofalgo}}
%   \centerline{EXAMPLE OF PROPOSED ALGORITHM}
%   \vskip5pt
%   \centering
%   \begin{tabular}{c|c|l|ccccccc}
%     \hline
%     \hline
%     \multicolumn{3}{c|}{\multirow{2}{*}{}}                                    & \multicolumn{7}{c}{Panels}                                                      \\ \cline{4-10} 
% \multicolumn{3}{c|}{}                                                     & P1  & P4  & P5                       & P2 & P3 & P7                     & P6     \\ \hline
% \multirow{3}{*}{Current Levels} & Q1 & \multirow{3}{*}{Number of modules} & 2   & 2   & 2                        & 1  & 1  & 1                      & 0      \\ \cline{2-2}
%                                 & Q2 &                                    & 2   & 2   & 2                        & 1  & 1  & 1                      & 1      \\ \cline{2-2}
%                                 & Q3 &                                    & 3   & 3   & 3                        & 2  & 2  & 2                      & 2      \\ \hline
% \multirow{2}{*}{Loss-rate}      & \multicolumn{2}{c|}{Loss-rate(p,Q1,Q2)} & 0   & 0   & \multicolumn{1}{c|}{0}   & 0  & 0  & \multicolumn{1}{c|}{0} & $\infty$ \\ \cline{2-3}
%                                 & \multicolumn{2}{c|}{Loss-rate(p,Q1,Q3)} & 0.5 & 0.5 & \multicolumn{1}{c|}{0.5} & 1  & 1  & \multicolumn{1}{c|}{1} & 1      \\ \hline
% \multicolumn{3}{c|}{Algorithm  priority}                                  & 1   & 2   & 3                        & 4  & 5  & 6                      & 7      \\ \hline
% \end{tabular}
% \end{table*}

@@

In the step~\ref{step:1}, un-selected PV panels are sorted  in a lexicographically  ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_{p}(Q_{n})$.
This sorting procedure gives a basic priority for all un-selected PV panels.
A panel with less ``$loss$'' and more modules for target current level are preferred.
The last sorting index $M_{p}(Q_{n})$ aim to minimize the number of selected PV modules for target current level $Q_{n}$, and it will be described in step~\ref{step:3}.
Moreover, according to equation~(\ref{eq:4}), the $Loss-rate$ is infinity for those PV panels who have no active modules.

@@

In the step~\ref{step:3}, the number of active PV modules and the number of selected panels are optimized.
As if selected PV panels contain active PV modules exceed required amount $m$, redundant panels will be removed if existed.
A PV panel is redundant if and only if the number of active PV module still meet requirement or more even if this panel has been removed.
This remove procedure starting from the last ``$loss$'' level, proposed algorithm will check $M_{p}Q_{n}$ for each panel $p$.
If the number of active modules still exceed $m$ after panel $p$ is removed, the same procedure will repeat until all redundant panels are removed or every panel have been checked.

\begin{algorithm}[htbp]
  \caption{Feasibility Problem}
  \label{sec:algorithm-1}
  \LinesNumbered
  \SetKwInOut{Input}{Input}
  \Input{
    \textit{$Q = (Q_{1}, Q_{2}, \ldots ,Q_{s}$)}: current sequence for given configuration; \\
    \textit{$m$}: the number of required active modules per-string;\\
    \textit{$M_{p}$}: the number of active modules in each panel \textit{p};\\
    \textit{s}: the number of strings;
  }
  \SetKwInOut{Output}{Output}
  \Output{
    Feasibility Result;
  }
  \For{\textup{each string} $ k (2 \leq k \leq s)$ \textup{and panel} $p$}{$Loss(p,k) = M_{p}(Q_{k}) - M_{p}(Q_{k-1})$}
  \For{j = 1 to s}
  {{\If{$\sum M_{p}(Q_{j})$ \textup{for unselected panels} $< m$}
      {\textup{\textbf{return :}} Feasibility = NO}}
    $PS$ = a set of unselected panels with $M_{p}(Q_{j}) > 0$;\\
     // \textbf{step \ref{step3}}\\
     sort $PS$ in a lexicographically ascending order of $Loss(p,j+1)$, $Loss(p,j+2)$, $\ldots$, $Loss(p,s)$, $M_{p}(Q_{j})$;\\
     // \textbf{step \ref{step4}}\\
     select panels in the order in $PS$ until $\sum M_{p}(Q_{j})$ for selected panels $\geq m$;\\
     // \textbf{step \ref{step5}}\\
     group selected panels $LV_{1}$, $LV_{2}$,$\ldots$, $LV_{h}$ with loss level ($LV_{1}$ is the lowest level);\\
     \For{i = h to 1}
     {find and cancel redundant panels in $LV_{i}$ in the order in $PS$}
     // \textbf{step \ref{step6}}\\
     \For{i = h to 1}
     {apply swap rules for selected panels in $LV_{i}$ and an unselected panel in the same loss level}
    }
    \textup{\textbf{return :}} Feasibility = YES
  \end{algorithm}

\section{Evaluation}\label{sec:evaluation}
\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.

>>>>

\subsection{Outline of the algorithm}\label{sec:outline-algorithm}
In a PV array with $s$ PV strings.
For a given current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s})$ $(Q_{i} \geq Q_{j} \mbox{\ if\ } i \leq j)$, we will assign PV panels to strings in the order of $Q_{1},Q_{2},\ldots ,Q_{s}$.
In this step, we will consider how much we lose an opportunity that the panel is more effectively used for the next current level.
For example, as the PV panel shown in Table~\ref{tab:NumofModules} which contain three PV modules.
2 of 3 modules are able to working at current level of $Q_{1}$ and $Q_{2}$.
All 3 modules are able to activate at current level $Q_{3}$.
Thus, if this panel been selected working for a PV string at current level $Q_{1 or 2}$ , two-third of modules are able to deliver energy while the remaining one module been bypassed.
We consider the ``$loss$'' that how many PV modules we fail to use in other current level and the ``$gain$'' that how many PV modules we can activate in the target current level together.
Since two parameter are considered in the selection process, they can minimize ``$loss$'' while minimizing the number of selected PV panels.
% In this algorithm, we select PV panels as so to minimize the $loss$ and maximize the $gain$.
\begin{table}[tbp]
  \caption[]{}
  \label{tab:NumofModules} 
  \centerline{Maximum number of activate PV modules}
  \vskip5pt
  \begin{center}
  \begin{tabular}{c|c|c|c}
    \hline
    Current level                 & $Q_{1}$ & $Q_{2}$ & $Q_{3}$  \\ \hline
    Number of activate PV modules & 2  & 2    & 3        \\ \hline
  \end{tabular}
  \end{center}
\end{table}
In this algorithm, we choose $Loss-rate$ to give selection priority.
The $Loss$-$rate$ is the difference of active modules in panel $p$ for the target current level $Q_{k^{'}}$  in current sequence $Q$ with other current levels per module.
Let $M_{p}(I)$ denote the number of PV modules that can be active at current level $I$ in panel $p$.
In a $s$ strings PV array, $Loss-rate$ for panel $p$ of target current level $k^{'}$ on $k$-th current level $Q_{k}$ ($2 \leq k \leq s$) is shown as follow.
\begin{equation}\label{eq:4}
    Loss\mbox{-}rate(p,k^{'},k) =
    \begin{cases}
    \frac{M_{p}(Q_{k})-M_{p}(Q_{k^{'}})}{M_{p}(Q_{k^{'}})} & \mbox{if } M_{p}(Q_{k^{'}}) \neq 0 \\
    \infty & \mbox{if } M_{p}(Q_{k^{'}}) = 0
  \end{cases}
\end{equation}

@@

To assign panels of target current level $k^{'}$ to $k^{'}$-th string, the following step are applied.
Let $m$ be the required number of active modules per-string.
\begin{enumerate}
  \item\label{step:1} Sort un-selected panels with ``$loss$'' and ``$gain$''.
% \item\label{step:1} Sort un-selected panels in a lexicographically ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_p(Q_n)$.
\item\label{step:2} Selects sorted panels one by one until reaching the required number of active modules $m$.
  % In step 2, panel with no active modules is skipped.
\item\label{step:3} Optimize the number of active modules.
  In step 3, if the number of selected active modules exceeds the required number $m$, redundant panels will be removed if exist.
\end{enumerate}
% \begin{table*}[h]
%   \caption[]{ \label{tab:Exampleofalgo}}
%   \centerline{EXAMPLE OF PROPOSED ALGORITHM}
%   \vskip5pt
%   \centering
%   \begin{tabular}{c|c|l|ccccccc}
%     \hline
%     \hline
%     \multicolumn{3}{c|}{\multirow{2}{*}{}}                                    & \multicolumn{7}{c}{Panels}                                                      \\ \cline{4-10} 
% \multicolumn{3}{c|}{}                                                     & P1  & P4  & P5                       & P2 & P3 & P7                     & P6     \\ \hline
% \multirow{3}{*}{Current Levels} & Q1 & \multirow{3}{*}{Number of modules} & 2   & 2   & 2                        & 1  & 1  & 1                      & 0      \\ \cline{2-2}
%                                 & Q2 &                                    & 2   & 2   & 2                        & 1  & 1  & 1                      & 1      \\ \cline{2-2}
%                                 & Q3 &                                    & 3   & 3   & 3                        & 2  & 2  & 2                      & 2      \\ \hline
% \multirow{2}{*}{Loss-rate}      & \multicolumn{2}{c|}{Loss-rate(p,Q1,Q2)} & 0   & 0   & \multicolumn{1}{c|}{0}   & 0  & 0  & \multicolumn{1}{c|}{0} & $\infty$ \\ \cline{2-3}
%                                 & \multicolumn{2}{c|}{Loss-rate(p,Q1,Q3)} & 0.5 & 0.5 & \multicolumn{1}{c|}{0.5} & 1  & 1  & \multicolumn{1}{c|}{1} & 1      \\ \hline
% \multicolumn{3}{c|}{Algorithm  priority}                                  & 1   & 2   & 3                        & 4  & 5  & 6                      & 7      \\ \hline
% \end{tabular}
% \end{table*}

@@

In the step~\ref{step:1}, un-selected PV panels are sorted  in a lexicographically  ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_{p}(Q_{k^{'}})$.
This sorting procedure gives a basic priority for all un-selected PV panels.
A panel with less ``$loss$'' and more modules for target current level are preferred.
The last sorting index $M_{p}(Q_{k^{'}})$ aim to minimize the number of selected PV modules for target current level $Q_{k^{'}}$, and it will be described in step~\ref{step:3}.
Moreover, according to equation~(\ref{eq:4}), the $Loss-rate$ is infinity for those PV panels who have no active modules.

@@

In the step~\ref{step:3}, the number of active PV modules and the number of selected panels are optimized.
As if selected PV panels contain active PV modules exceed required amount $m$, redundant panels will be removed if existed.
A PV panel is redundant if and only if the number of active PV module still meet requirement or more even if this panel has been removed.
This remove procedure starting from the last ``$loss$'' level, proposed algorithm will check $M_{p}Q_{k^{'}}$ for each panel $p$.
If the number of active modules still exceed $m$ after panel $p$ is removed, the same procedure will repeat until all redundant panels are removed or every panel have been checked.

\begin{algorithm}[htbp]
  \caption{Feasibility Problem}
  \label{sec:algorithm-1}
  \LinesNumbered
  \SetKwInOut{Input}{Input}
  \Input{
    \textit{$Q = (Q_{1}, Q_{2}, \ldots ,Q_{s}$)}: current sequence for given configuration; \\
    \textit{$m$}: the number of required active modules per-string;\\
    \textit{$M_{p}$}: the number of active modules in each panel $p$;\\
    \textit{s}: the number of strings;
  }
  \SetKwInOut{Output}{Output}
  \Output{
    Feasibility Result;
  }
  \For{\textup{each target current level} $Q_{k}$ $(1 \leq k \leq s)$ \textup{and each panel} $p$}
  {
    \uIf{$\sum M_{p}(Q_{k})$ $<$ $m$}
    {\textup{\textbf{return :}} Feasibility = NO\\
    \tcc{Not enough active modules to meet requirement}}
    \Else{$Loss-rate(p,k,k+1) = (M_{p}(Q_{k+1}) - M_{p}(Q_{k}))/M_{p}(Q_{k})$}
  }

  \For{\textup{each} target current level $Q_{k}$}
  {
    % {\If{$\sum M_{p}(Q_{j})$ \textup{for unselected panels} $< m$}
    %   {\textup{\textbf{return :}} Feasibility = NO}}
    $P$ = a set of un-selected panels with $M_{p}(Q_{k})$;\\
     \tcp{\textbf{step~\ref{step:1}}}
     Sort $PS$ in a lexicographically ascending order of $Loss-rate$ and descending order of $M_{P}(Q_{j})$\\
     % $Loss(p,j+2)$, $\ldots$, $Loss(p,s)$, $M_{p}(Q_{j})$;\\
     \tcp{\textbf{step~\ref{step:2}}}
     select panels in the order in $PS$ until $\sum M_{p}(Q_{j})$ for selected panels $\geq m$;\\
     % \If{$\sum M_{p}(Q_{j})$ \textup{for selected panels} = $m$}
     % {\textup{\textbf{return :}} Feasibility = YES}
     \tcp{\textbf{step~\ref{step:3}}}
     group selected panels into ``$loss$'' levels ($LV_{1}$, $LV_{2}$,$\ldots$, $LV_{h}$) based on $Loss-rate$ ascending order.\\
     \For{i = h to 1}
     {
       find and remove redundant panels in ``$loss$'' level $LV_{i}$
     }
     % // \textbf{step \ref{step6}}\\b
     % \For{i = h to 1}
     % {apply swap rules for selected panels in $LV_{i}$ and an unselected panel in the same loss level}
    }
    \textup{\textbf{return :}} Feasibility = YES
  \end{algorithm}

\section{Evaluation}\label{sec:evaluation}
\subsection{Algorithm time complexity}
In proposed algorithm, first, $Loss-rate(p,k^{'},k)$ is evaluated for all PV panel $p$ and target current level $Q_{k^{'}}$ with other current level $Q_{k}$.
This step takes $O(sn)$ where is $n$ is the number of panels and $s$ is the number of PV strings.
Then the algorithm iterate as follows:
\begin{enumerate}
\item\label{item:1} Sort panels by $Loss-rate$ and $M_{P}(Q_{k^{'}})$
\item\label{item:2} Select initial panels
\item\label{item:3} Remove redundant panels
\end{enumerate}

\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.
